The great codivergence bake off

### 2024-12-05 manuscript/ms.tex
Adding some temporary page breaks.
Adding page breaks to make sections in PDF easier to delineate.
Adding information about empirical datasets in Methods

\author[1]{Tanner Myers}
\author[1]{Randy Klabacka}
\author[1]{Hailey Whitaker}
\author[1]{Tashitso Anamza}
\author[1]{Claire Tracy}
\author[1]{Jamie R.\ Oaks \thanks{Corresponding author: \href{mailto:joaks@auburn.edu}{\tt joaks@auburn.edu}}}
\affil[1]{Department of Biological Sciences \& Museum of Natural History, Auburn University, Auburn, Alabama 36849}

@@

To assess the effect of a using a full-likelihood approach, we reanalyzed two
datasets with previously published results of using the ABC approach to
estimating shared divergence times.

In their study into the factors affecting the divergence of flightless darkling
beetles across the Aegean Archipelago,
Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to
estimate the relative divergence times of 13 pairs of populations.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

To test the prediction of clustered divergences driven by Pleistocene glacial
cycles Oaks et al.\ \citeyear{Oaks2012} used MTML-msBayes \cite{Huang2011} to
estimate the divergence times of 22 pairs of populations from across the
Philippine Islands.
Oaks \citeyear{Oaks2014dpp} reanalyzed these same data using \dppmsbayes.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

@@

>>>>

\author[1]{Tanner C.\ Myers}
\author[1]{Randy Klabacka}
\author[1]{Hailey Whitaker}
\author[1]{Tashitso Anamza}
\author[1]{Claire Tracy}
\author[1]{Jamie R.\ Oaks \thanks{Corresponding author: \href{mailto:joaks@auburn.edu}{\tt joaks@auburn.edu}}}
\affil[1]{Department of Biological Sciences \& Museum of Natural History, Auburn University, Auburn, Alabama 36849}

@@

To assess the effect of a using a full-likelihood approach, we reanalyzed two
datasets with previously published results of using the ABC approach to
estimate shared divergence times.

In their study into the factors affecting the divergence of flightless darkling beetles across the Aegean Archipelago,
Papadopoulou and Knowles \citeyear{PapadopoulouKnowles2015} used \dppmsbayes to estimate the relative divergence times of 13 pairs of populations that vary phenotypically and ecologically.
Their dataset included two Sanger loci --- one mitochondrial (Cox1; \textit{n} = 403) and one nuclear (Mp20; \textit{n} = 273)--- sequenced across hundreds of beetles from 60 localities on the 11 islands on the Cycladic plateau in the Aegean archipelago \citep{PapadopoulouKnowles2015}.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

To test the prediction of clustered divergences driven by Pleistocene glacial
cycles Oaks et al.\ \citeyear{Oaks2012} used MTML-msBayes \citep{Huang2011} to
estimate the divergence times of 22 pairs of vertebrate populations from across the
Philippine Islands.
Oaks \citeyear{Oaks2014dpp} reanalyzed these same data using \dppmsbayes.
This dataset consists of one or two mitochondrial loci gathered from closely related species or populations within species distributed across contemporarily isolated islands that previous were contiguous.
\jrocomment{We should probably describe the dataset a bit; number of loci, etc.}

@@

% We can remove this page break later, just adding it now to make it easier to
% delineate empirical results in the PDF
\newpage
